---
title: "greedyBAPs"
author: "Christopher Nowzohour"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{greedyBAPs}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

Link to arxiv paper https://arxiv.org/abs/1508.01717

## Simulation

We can generate uniform BAPs, parameters, and data as follows:
```{r, fig.show='hold'}
library(greedyBAPs)
set.seed(1)
bap <- generateUniformBAP(p = 4, N = 1)[[1]]
params <- generateBAPPArameters(bap)
data <- generateData(n = 100, params = params)
plotBAP(bap)
pairs(data)
```

## Running Greedy Search
We can run greedy search and plot scores curves as follows:
```{r}
res <- greedySearch(data, n.restarts = 10, mc.cores = 4)
plotScoreCurves(res$all.scores, res$times)
```

## Causal Effects Simulation
We can run the causal effects simulation and plot ROC curves as follows:
__for some reason this fails - fix later__
```{r}
# res <- causalEffectsSimulation(N = 10, p = 5, n = 1000, mc.cores = 4, n.restarts = 10, max.in.degree = 2, max.steps = 100, max.iter.ricf = 10, equivalent.eps = 1e-10)
# plotROCCurve(res$CE.gt, res$CE.greedy)
```

## Sachs data
We can run DAG-search on one of the Sachs datasets as follows:
```{r}
data.sachs <- as.matrix(flowCytometry[flowCytometry$source == unique(flowCytometry$source)[1], 1:11])
res <- greedySearch(data.sachs, n.restarts = 10, mc.cores = 4, dags.only = TRUE)
plotScoreCurves(res$all.scores, res$times)
```



The `html_vignette` template includes a basic CSS theme. To override this theme you can specify your own CSS in the document metadata as follows:

    output: 
      rmarkdown::html_vignette:
        css: mystyles.css

## Figures

The figure sizes have been customised so that you can easily put two images side-by-side. 

```{r, fig.show='hold'}
plot(1:10)
plot(10:1)
```

You can enable figure captions by `fig_caption: yes` in YAML:

    output:
      rmarkdown::html_vignette:
        fig_caption: yes

Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**.

## More Examples

You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(mtcars, 10))
```

Also a quote using `>`:

> "He who gives up [code] safety for [code] speed deserves neither."
([via](https://twitter.com/hadleywickham/status/504368538874703872))
