---
title: "greedyBAPs"
author: "Christopher Nowzohour"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{greedyBAPs}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---


This package implements greedy search for a class of graphical models called bow-free acyclic path diagrams (BAPs). For more information and theoretical results, see the paper https://arxiv.org/abs/1508.01717

Generally, the functionality provided by this package can be split into the following categories:

* Basic Simulation: random graphs (`generateUniformBAP`), parameters (`generateBAPPArameters`), data (`generateData`)
* Greedy Search: finding the best fitting graph given data (`greedySearch`)
* Simulation Experiments: causal effects recovery (`causalEffectsSimulation`)
* Visualisation: graphs (`plotBAP`), greedy search scores (`plotScoreCurves`), causal effects ROC curve (`plotROCCurve`)

## Data Structures

### Graphs

A graph is represented via its adjacency matrix $M$ in a similar way as for `ggm::makeMG`. In particular:

* $M_{ij} = 0$ means there is no edge between nodes $i$ and $j$
* $M_{ij} = 1$ means there is an edge $i \rightarrow j$
* $M_{ij} = 100$ means there is an edge $i \leftrightarrow j$

```{r}
library(greedyBAPs)
M <- t(cbind(
  c(0, 1, 100),
  c(0, 0, 0),
  c(0, 0, 0)
))
plotBAP(M)
```

### Parameters
A BAP model is as a linear recursive structural equation model with (correlated) Gaussian noise. If $\mathbf{X}$ is the variable vector, the BAP can be written as:

$\mathbf{X} = B^T \mathbf{X} + \epsilon$

where $({B})_{ij}$ is the edge weight of edge $i \rightarrow j$, and $\epsilon$ has a $\mathcal{N}(0, \Omega)$ distribution.

For the example above, a valid parametrisation would be:

```{r}
B <- t(cbind(
  c(0, 0.3, 0),
  c(0, 0, 0),
  c(0, 0, 0)
))
Omega <- t(cbind(
  c(3, 0, 1.5),
  c(0, 2, 0),
  c(0, 0, 1)
))
```

### Data

An $n$-sample dataset for a $p$-dimensional BAP model has to be in the form of an $n$-by-$p$ matrix. For example, we could fit the following dataset to the model above (it would be a poor fit, because the data was not generated from this model):

```{r}
n <- 100
p <- 3
data <- matrix(rnorm(n * p), n, p)
```

## Examples

### Randomly generating BAPs (uniformly), parameters, data

```{r, fig.show='hold'}
set.seed(1)
bap <- generateUniformBAP(p = 4, N = 1)[[1]]
params <- generateBAPParameters(bap)
data <- generateData(n = 100, params = params)
plotBAP(bap)
pairs(data)
```

### Running greedy search and visualising scores

```{r}
res <- greedySearch(data, n.restarts = 10, mc.cores = 4)
plotScoreCurves(res$all.scores, res$times)
```

### Causal effects simulation experiment

```{r}
res <- causalEffectsSimulation(N = 10, p = 5, n = 1000, mc.cores = 4, n.restarts = 10, max.in.degree = 2, max.steps = 100, max.iter.ricf = 10, equivalent.eps = 1e-10)
roc <- plotROCCurve(res$CE.gt, res$CE.greedy)
```

### Genomic data

This package ships with a dataset from Sachs et al. (2015)^[http://science.sciencemag.org/content/308/5721/523], to which DAGs can be fit as follows:

```{r}
data.sachs <- as.matrix(flowCytometry[flowCytometry$source == unique(flowCytometry$source)[1], 1:11])
res <- greedySearch(data.sachs, n.restarts = 10, mc.cores = 4, dags.only = TRUE)
plotScoreCurves(res$all.scores, res$times)
```
